\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot,
    top=2 cm,
    bottom=2 cm,
    left=2 cm,
    right=2 cm,
    footskip=1.0 cm,
]{geometry}
\usepackage[explicit]{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 79, 144}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{hyperref}
\hypersetup{
    pdftitle={Omar Essam El-Din Mohamed's CV},
    pdfauthor={Omar Essam El-Din Mohamed},
    colorlinks=true,
    urlcolor=primaryColor
}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}

\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}

% Section Formatting
\titleformat{\section}{\LARGE\bfseries\color{primaryColor}}{}{0em}{}[\vspace{0.2em}\titlerule]
\titlespacing{\section}{0pt}{1em}{0.5em}

\begin{document}
    \begin{center}
        {\LARGE \textbf{Omar Essam El-Din Mohamed}} \\
        {Zahraa El Maadi, Cairo, Egypt} \\
        {\faPhone* \hspace{0.2cm} +20 1004819774} \hspace{1cm}
        {\href{mailto:eng.omar.e@gmail.com}{\faEnvelope[regular] \hspace{0.2cm} Email}} \hspace{1cm}
        {\href{https://github.com/omare32}{\faGithub \hspace{0.2cm} GitHub}}
    \end{center}
    
    \section{Professional Summary}
    A versatile Project Management Information Systems (PMIS) Engineer with extensive experience in construction, civil engineering, and data engineering. Proven expertise in project control, programming, and data science, with a strong ability to automate tasks and optimize workflows. Dedicated to delivering efficient solutions under tight deadlines and improving team performance.
    
    \section{Education}
    \textbf{Cairo University}, Bachelor of Science in Civil Engineering, May 2013 \\
    \textit{Overall Grade:} Good (C) \hspace{1cm} \textit{Project Grade:} Excellent (A) \hspace{1cm} \textit{Graduation Project:} Steel Bridges Design \\
    \textbf{Orouba Language School}, Graduation Score: 98.9\% (405.5/410)
    
    \section{Professional Experience}
    \textbf{Programming and Data Engineering Experience}
    \begin{itemize}[leftmargin=*]
        \item \textbf{Data Engineer Lead} | Rowad Modern Engineering (Aug 2024 – Present)
        \begin{itemize}[leftmargin=1cm]
            \item Established a data warehouse team and integrated data sources for improved reporting.
        \end{itemize}
        \item \textbf{Data Scientist} | Rowad Modern Engineering (Mar 2024 – Jul 2024)
        \begin{itemize}[leftmargin=1cm]
            \item Developed machine learning models for cash flow predictions.
        \end{itemize}
        \item \textbf{Senior Data Engineer} | Rowad Modern Engineering (Apr 2023 – Dec 2023)
        \begin{itemize}[leftmargin=1cm]
            \item Automated repetitive tasks using Python, saving significant resource hours.
        \end{itemize}
        \item \textbf{IT Networking / Data Engineer} | Rowad Modern Engineering (Jan 2023 – Present)
        \begin{itemize}[leftmargin=1cm]
            \item Maintained SQL and MySQL databases, ensuring seamless data access and storage.
        \end{itemize}
        \item \textbf{Co-Owner} | Cyber Cafe (2009 – 2011)
        \begin{itemize}[leftmargin=1cm]
            \item Managed hardware and networking for all systems.
        \end{itemize}
    \end{itemize}

    \textbf{Construction and Civil Engineering Experience}
    \begin{itemize}[leftmargin=*]
        \item \textbf{Project Control Section Head} | Rowad Modern Engineering, Bridges Sector (Sep 2021 – May 2023)
        \begin{itemize}[leftmargin=1cm]
            \item Managed the project control team for bridge projects. Streamlined cost and schedule reporting processes. Enhanced coordination between construction and planning teams.
        \end{itemize}
        \item \textbf{Senior Project Control Engineer} | Rowad Modern Engineering, Head Office (Jan 2019 – Aug 2021)
        \begin{itemize}[leftmargin=1cm]
            \item Oversaw multiple project schedules and cost control measures. Delivered periodic project performance reports to stakeholders.
        \end{itemize}
        \item \textbf{Project Control Engineer} | Rowad Modern Engineering (Apr 2018 – Dec 2018)
        \begin{itemize}[leftmargin=1cm]
            \item Worked on major infrastructure projects including Nefisha Bridge and El Sokhna Tunnel.
        \end{itemize}
        \item \textbf{Tendering Engineer} | Rowad Modern Engineering, Tender Department (Jan 2018 – Mar 2018)
        \begin{itemize}[leftmargin=1cm]
            \item Evaluated project tenders for technical and financial feasibility.
        \end{itemize}
        \item \textbf{Planning/Cost Control Engineer} | Concrete Plus (Apr 2015 – Jan 2018)
        \begin{itemize}[leftmargin=1cm]
            \item Coordinated cost control for multiple projects from the head office.
        \end{itemize}
        \item \textbf{Site Engineer} | Concrete Plus, Porto October Project (Apr 2014 – Mar 2015)
        \begin{itemize}[leftmargin=1cm]
            \item Supervised on-site construction activities, ensuring compliance with design specifications.
        \end{itemize}
    \end{itemize}

    \section{Key Skills}
    \begin{itemize}[leftmargin=*]
        \item \textbf{Technical Tools:} Primavera P6, MS Project, Synchro, Revit, Navisworks, Power BI, AutoCAD
        \item \textbf{Programming:} Python, SQL, Java, C++ (familiar), C\# (familiar)
        \item \textbf{Data Engineering:} ETL pipelines, Airflow, Spark, ERP systems
        \item \textbf{Software:} Microsoft Office (expert in Excel), Adobe Photoshop, Illustrator, After Effects
        \item \textbf{Construction Expertise:} Cost control, tender evaluation, risk management
        \item \textbf{Languages:} Arabic (Native), English (Fluent)
    \end{itemize}
    
    \section{Certifications}
    \begin{itemize}[leftmargin=*]
        \item Certified Data Scientist Professional (Epsilon AI)
        \item Primavera P6
        \item Python Programming
        \item PMP Certification
        \item CCNA and CCNP Networking
        \item Steel Bridges Design
    \end{itemize}

\end{document}
